---
title: "Regression Models Course Project"
author: "nthehai01"
date: "3/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Project Introduction

In this project, I will work for **Motor Trend**, a magazine about the automobile industry. Looking at the ```mtcars``` data set, I am interested i exploring the relationship between a set of variables and miles per gallon as an outcome. I am particularly interested in the following two questions:

* “Is an automatic or manual transmission better for MPG”
* "Quantify the MPG difference between automatic and manual transmissions"

## EDA

Loading data set
```{r}
data("mtcars")
head(mtcars)
```

Transforming some features into factors
```{r}
mtcars$cyl <- factor(mtcars$cyl)
mtcars$vs <- factor(mtcars$vs)
mtcars$am <- factor(mtcars$am)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
```

Summarizing data
```{r}
summary(mtcars)
```

Boxplot showing the difference number of miles per gallon between automatic and manual vehicles
```{r}
library(ggplot2)
dif <- ggplot(mtcars, aes(x = am, y = mpg)) +
    geom_boxplot() +
    scale_x_discrete(labels = c("Automatic", "Manual")) + 
    xlab("Types of vehicles") +
    ylab("Miles per gallon") +
    ggtitle("MPG that automatic and manual vehicles consume")
dif 
```


## Regression Analysis

*Qualify the difference in MPG that each type of vehicles consume*
```{r}
aggregate(mpg ~ am, data = mtcars, mean)
```

We can see that overall, the for 1 gallon, the automatic cars can go more than almost  7 gallon compared to the manual cars.

*Now, I will use t-test to determine what I have just denoted is true:*
```{r}
automatic.cars <- mtcars[mtcars$am == 0, ]
manual.cars <- mtcars[mtcars$am == 1, ]

t.test(manual.cars$mpg, automatic.cars$mpg, 
       alternative = "greater")
```

The p-value is less than 0.05, thus we can state this is a significant difference.

```{r}
init <- lm(mpg ~ am, data = mtcars)
summary(init)

betterFit <- lm(mpg ~ am + cyl + disp + hp + wt, data = mtcars)
anova(init, betterFit)
```


#### Find the model that best predicting the MPG

*Fit the simplest model with only the type of vehicles is the predictor:*
```{r}
sim.model <- lm(mpg ~ am, data = mtcars)
summary(sim.model)
```

The $R^2$ is less than $36$%. It means the type of vehicles helps us explain only $36$% of the variance, thus it is not enough good for predicting a new MPG of a new car. We need to fit a multivariate model.

*First, we need to draw a pair plot to determine which features have the strongest correlation with the ```mpg```:*
```{r}
pairs(mpg ~ ., data = mtcars)
```

From the graph above, we can see that the ```cyl```, ```disp```, ```hp```, ```wt``` have the strongest correlation with ```mpg```.

*Now, we fit the new model with ```cyl```, ```disp```, ```hp```, ```wt``` features as the predictors:*
```{r}
mul.model <- lm(mpg ~ am + cyl + disp + hp + wt, data = mtcars)
summary(mul.model)
```

The $R^2$ is $87$% which is very high compared to the $R^2$ of the previous one-variable model.

*Using ```anova``` function to comapare the two models:*
```{r}
anova(sim.model, mul.model)
```

The p-value is less than 0.05, we can claim that the multivariate model ```mul.model``` is better than ```sim.model```.